---
title: "R packages by L. Collado-Torres"
author:
  - name: Leonardo Collado-Torres
    affiliation:
    - &libd Lieber Institute for Brain Development, Johns Hopkins Medical Campus
    - &ccb Center for Computational Biology, Johns Hopkins University
    email: lcolladotor@gmail.com
output:
  html_document:
    includes:
      in_header: header.html
    self_contained: false
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
abstract: |
  I like to check my R packages using GitHub Actions, Bioconductor and other
  tools. This small website helps me see the status of the packages I've made
  without having to navigate to a bunch of other websites. This website also
  helps me keep track of project repositories I've made where users might
  ask questions.
vignette: |
  %\VignetteIndexEntry{R packages by L. Collado-Torres}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
library("BiocStyle")
library("sessioninfo")
```

# Bioconductor

## Maintainer

### Software

* `r Biocpkg("biocthis")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/biocthis.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/biocthis)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/biocthis.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/biocthis)
[![Codecov test coverage](https://codecov.io/gh/lcolladotor/biocthis/branch/devel/graph/badge.svg)](https://codecov.io/gh/lcolladotor/biocthis?branch=devel)
[![R build status](https://github.com/lcolladotor/biocthis/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/lcolladotor/biocthis/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/biocthis.svg)](https://support.bioconductor.org/tag/biocthis/)
[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/biocthis)](https://github.com/lcolladotor/biocthis/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/biocthis)](https://github.com/lcolladotor/biocthis/pulls)

* `r Biocpkg("derfinder")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/derfinder.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/derfinder)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/derfinder.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/derfinder)
[![Codecov test coverage](https://codecov.io/gh/lcolladotor/derfinder/branch/devel/graph/badge.svg)](https://codecov.io/gh/lcolladotor/derfinder?branch=devel)
[![R build status](https://github.com/lcolladotor/derfinder/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/lcolladotor/derfinder/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/derfinder.svg)](https://support.bioconductor.org/tag/derfinder/)
[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/derfinder)](https://github.com/lcolladotor/derfinder/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/derfinder)](https://github.com/lcolladotor/derfinder/pulls)

* `r Biocpkg("derfinderHelper")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/derfinderHelper.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/derfinderHelper)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/derfinderHelper.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/derfinderHelper)
[![Codecov test coverage](https://codecov.io/gh/leekgroup/derfinderHelper/branch/devel/graph/badge.svg)](https://codecov.io/gh/leekgroup/derfinderHelper?branch=devel)
[![R build status](https://github.com/leekgroup/derfinderHelper/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/leekgroup/derfinderHelper/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/derfinderHelper.svg)](https://support.bioconductor.org/tag/derfinderHelper/)
[![GitHub issues](https://img.shields.io/github/issues/leekgroup/derfinderHelper)](https://github.com/leekgroup/derfinderHelper/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/derfinderHelper)](https://github.com/leekgroup/derfinderHelper/pulls)

* `r Biocpkg("derfinderPlot")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/derfinderPlot.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/derfinderPlot)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/derfinderPlot.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/derfinderPlot)
[![Codecov test coverage](https://codecov.io/gh/leekgroup/derfinderPlot/branch/devel/graph/badge.svg)](https://codecov.io/gh/leekgroup/derfinderPlot?branch=devel)
[![R build status](https://github.com/leekgroup/derfinderPlot/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/leekgroup/derfinderPlot/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/derfinderPlot.svg)](https://support.bioconductor.org/tag/derfinderPlot/)
[![GitHub issues](https://img.shields.io/github/issues/leekgroup/derfinderPlot)](https://github.com/leekgroup/derfinderPlot/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/derfinderPlot)](https://github.com/leekgroup/derfinderPlot/pulls)

* `r Biocpkg("megadepth")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/megadepth.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/megadepth)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/megadepth.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/megadepth)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/megadepth/branch/devel/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/megadepth?branch=devel)
[![R build status](https://github.com/LieberInstitute/megadepth/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/megadepth/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/megadepth.svg)](https://support.bioconductor.org/tag/megadepth/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/megadepth)](https://github.com/LieberInstitute/megadepth/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/megadepth)](https://github.com/LieberInstitute/megadepth/pulls)

* `r Biocpkg("recount")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/recount.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/recount)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/recount.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/recount)
[![Codecov test coverage](https://codecov.io/gh/leekgroup/recount/branch/devel/graph/badge.svg)](https://codecov.io/gh/leekgroup/recount?branch=devel)
[![R build status](https://github.com/leekgroup/recount/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/leekgroup/recount/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/recount.svg)](https://support.bioconductor.org/tag/recount/)
[![GitHub issues](https://img.shields.io/github/issues/leekgroup/recount)](https://github.com/leekgroup/recount/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/recount)](https://github.com/leekgroup/recount/pulls)

* `r Biocpkg("recount3")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/recount3.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/recount3)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/recount3.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/recount3)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/recount3/branch/devel/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/recount3?branch=devel)
[![R build status](https://github.com/LieberInstitute/recount3/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/recount3/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/recount3.svg)](https://support.bioconductor.org/tag/recount3/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recount3)](https://github.com/LieberInstitute/recount3/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/recount3)](https://github.com/LieberInstitute/recount3/pulls)

* `r Biocpkg("regionReport")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/regionReport.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/regionReport)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/regionReport.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/regionReport)
[![R build status](https://github.com/leekgroup/regionReport/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/leekgroup/regionReport/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/regionReport.svg)](https://support.bioconductor.org/tag/regionReport/)
[![GitHub issues](https://img.shields.io/github/issues/leekgroup/regionReport)](https://github.com/leekgroup/regionReport/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/regionReport)](https://github.com/leekgroup/regionReport/pulls)

### Annotation

* `r Biocpkg("GenomicState")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://bioconductor.org/images/shields/availability/all.svg)](http://bioconductor.org/packages/release/data/annotation/html/GenomicState.html#archives)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/GenomicState/branch/devel/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/GenomicState?branch=devel)
[![R build status](https://github.com/LieberInstitute/GenomicState/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/GenomicState/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/GenomicState.svg)](https://support.bioconductor.org/tag/GenomicState/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/GenomicState)](https://github.com/LieberInstitute/GenomicState/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/GenomicState)](https://github.com/LieberInstitute/GenomicState/pulls)

### Experiment data

* `r Biocpkg("derfinderData")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://bioconductor.org/shields/build/release/data-experiment/derfinderData.svg)](http://bioconductor.org/checkResults/release/data-experiment-LATEST/derfinderData/)
[![BioC dev status](http://bioconductor.org/shields/build/devel/data-experiment/derfinderData.svg)](http://bioconductor.org/checkResults/devel/data-experiment-LATEST/derfinderData/)
[![R build status](https://github.com/leekgroup/derfinderData/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/leekgroup/derfinderData/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/derfinderData.svg)](https://support.bioconductor.org/tag/derfinderData/)
[![GitHub issues](https://img.shields.io/github/issues/leekgroup/derfinderData)](https://github.com/leekgroup/derfinderData/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/derfinderData)](https://github.com/leekgroup/derfinderData/pulls)

* `r Biocpkg("spatialLIBD")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://bioconductor.org/shields/build/release/data-experiment/spatialLIBD.svg)](http://bioconductor.org/checkResults/release/data-experiment-LATEST/spatialLIBD/)
[![BioC dev status](http://bioconductor.org/shields/build/devel/data-experiment/spatialLIBD.svg)](http://bioconductor.org/checkResults/devel/data-experiment-LATEST/spatialLIBD/)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/spatialLIBD/branch/devel/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/spatialLIBD?branch=devel)
[![R build status](https://github.com/LieberInstitute/spatialLIBD/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/spatialLIBD/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/spatialLIBD.svg)](https://support.bioconductor.org/tag/spatialLIBD/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/spatialLIBD)](https://github.com/LieberInstitute/spatialLIBD/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/spatialLIBD)](https://github.com/LieberInstitute/spatialLIBD/pulls)

### Workflow

* `r Biocpkg("recountWorkflow")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/workflows/recountWorkflow.svg)](http://bioconductor.org/checkResults/release/workflows-LATEST/recountWorkflow/)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/workflows/recountWorkflow.svg)](http://bioconductor.org/checkResults/devel/workflows-LATEST/recountWorkflow/)
[![R build status](https://github.com/LieberInstitute/recountWorkflow/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/recountWorkflow/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/recountWorkflow.svg)](https://support.bioconductor.org/tag/recountWorkflow/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recountWorkflow)](https://github.com/LieberInstitute/recountWorkflow/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/recountWorkflow)](https://github.com/LieberInstitute/recountWorkflow/pulls)

## Contributor

* `r Biocpkg("DeconvoBuddies")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/DeconvoBuddies.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/DeconvoBuddies)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/DeconvoBuddies.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/DeconvoBuddies)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/DeconvoBuddies/branch/devel/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/DeconvoBuddies?branch=devel)
[![R build status](https://github.com/LieberInstitute/DeconvoBuddies/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/DeconvoBuddies/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/DeconvoBuddies.svg)](https://support.bioconductor.org/tag/DeconvoBuddies/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/DeconvoBuddies)](https://github.com/LieberInstitute/DeconvoBuddies/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/DeconvoBuddies)](https://github.com/LieberInstitute/DeconvoBuddies/pulls)

* `r Biocpkg("qsvaR")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/qsvaR.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/qsvaR)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/qsvaR.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/qsvaR)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/qsvaR/branch/devel/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/qsvaR?branch=devel)
[![R build status](https://github.com/LieberInstitute/qsvaR/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/qsvaR/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/qsvaR.svg)](https://support.bioconductor.org/tag/qsvaR/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/qsvaR)](https://github.com/LieberInstitute/qsvaR/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/qsvaR)](https://github.com/LieberInstitute/qsvaR/pulls)

* `r Biocpkg("smokingMouse")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://bioconductor.org/shields/build/release/data-experiment/smokingMouse.svg)](http://bioconductor.org/checkResults/release/data-experiment-LATEST/smokingMouse/)
[![BioC dev status](http://bioconductor.org/shields/build/devel/data-experiment/smokingMouse.svg)](http://bioconductor.org/checkResults/devel/data-experiment-LATEST/smokingMouse/)
[![R build status](https://github.com/LieberInstitute/smokingMouse/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/smokingMouse/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/smokingMouse.svg)](https://support.bioconductor.org/tag/smokingMouse/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/smokingMouse)](https://github.com/LieberInstitute/smokingMouse/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/smokingMouse)](https://github.com/LieberInstitute/smokingMouse/pulls)

* `r Biocpkg("TREG")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/TREG.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/TREG)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/TREG.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/TREG)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/TREG/branch/devel/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/TREG?branch=devel)
[![R build status](https://github.com/LieberInstitute/TREG/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/TREG/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/TREG.svg)](https://support.bioconductor.org/tag/TREG/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/TREG)](https://github.com/LieberInstitute/TREG/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/TREG)](https://github.com/LieberInstitute/TREG/pulls)

* `r Biocpkg("visiumStitched")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/visiumStitched.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/visiumStitched)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/visiumStitched.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/visiumStitched)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/visiumStitched/branch/devel/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/visiumStitched?branch=devel)
[![R build status](https://github.com/LieberInstitute/visiumStitched/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/visiumStitched/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/visiumStitched.svg)](https://support.bioconductor.org/tag/visiumStitched/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/visiumStitched)](https://github.com/LieberInstitute/visiumStitched/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/visiumStitched)](https://github.com/LieberInstitute/visiumStitched/pulls)

## [CDSB](https://comunidadbioinfo.github.io/) Mexico

* `r Biocpkg("regutools")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/regutools.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/regutools)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/regutools.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/regutools)
[![Codecov test coverage](https://codecov.io/gh/ComunidadBioInfo/regutools/branch/devel/graph/badge.svg)](https://codecov.io/gh/ComunidadBioInfo/regutools?branch=devel)
[![R build status](https://github.com/ComunidadBioInfo/regutools/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/ComunidadBioInfo/regutools/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/regutools.svg)](https://support.bioconductor.org/tag/regutools/)
[![GitHub issues](https://img.shields.io/github/issues/comunidadbioinfo/regutools)](https://github.com/comunidadbioinfo/regutools/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/comunidadbioinfo/regutools)](https://github.com/comunidadbioinfo/regutools/pulls)

# GitHub

## Actively maintained

* `r Githubpkg("lmweber/BestPracticesST")`

[![GitHub issues](https://img.shields.io/github/issues/lmweber/BestPracticesST)](https://github.com/lmweber/BestPracticesST/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lmweber/BestPracticesST)](https://github.com/lmweber/BestPracticesST/pulls)


* `r Githubpkg("LieberInstitute/jaffelab")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![R build status](https://github.com/LieberInstitute/jaffelab/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/jaffelab/actions/workflows/check-bioc.yml)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/jaffelab)](https://github.com/LieberInstitute/jaffelab/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/jaffelab)](https://github.com/LieberInstitute/jaffelab/pulls)

## Historical packages

* `r Biocpkg("brainflowprobes")`

<!--
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/brainflowprobes.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/brainflowprobes)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/brainflowprobes.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/brainflowprobes)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/brainflowprobes/branch/devel/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/brainflowprobes?branch=devel)
[![R build status](https://github.com/LieberInstitute/brainflowprobes/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/brainflowprobes/actions/workflows/check-bioc.yml)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/brainflowprobes.svg)](https://support.bioconductor.org/tag/brainflowprobes/)
-->
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/brainflowprobes)](https://github.com/LieberInstitute/brainflowprobes/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/brainflowprobes)](https://github.com/LieberInstitute/brainflowprobes/pulls)


* `r Githubpkg("lcolladotor/dots")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/dots)](https://github.com/lcolladotor/dots/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/dots)](https://github.com/lcolladotor/dots/pulls)

* `r Githubpkg("comunidadbioinfo/easyweb")`

[![GitHub issues](https://img.shields.io/github/issues/comunidadbioinfo/easyweb)](https://github.com/comunidadbioinfo/easyweb/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/comunidadbioinfo/easyweb)](https://github.com/comunidadbioinfo/easyweb/pulls)

* `r Githubpkg("leekgroup/enrichedRanges")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/enrichedRanges)](https://github.com/leekgroup/enrichedRanges/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/enrichedRanges)](https://github.com/leekgroup/enrichedRanges/pulls)

<!--
* `r Githubpkg("LieberInstitute/libdRSE")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/libdRSE)](https://github.com/LieberInstitute/libdRSE/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/libdRSE)](https://github.com/LieberInstitute/libdRSE/pulls)
-->

* `r Githubpkg("LieberInstitute/sgejobs")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![R build status](https://github.com/LieberInstitute/sgejobs/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/sgejobs/actions/workflows/check-bioc.yml)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/sgejobs)](https://github.com/LieberInstitute/sgejobs/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/sgejobs)](https://github.com/LieberInstitute/sgejobs/pulls)

* `r Githubpkg("LieberInstitute/shinycsv")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![R build status](https://github.com/LieberInstitute/shinycsv/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/LieberInstitute/shinycsv/actions/workflows/check-bioc.yml)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/shinycsv)](https://github.com/LieberInstitute/shinycsv/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/shinycsv)](https://github.com/LieberInstitute/shinycsv/pulls)

# Non R-packages

Note: some of these GitHub repositories are currently private but will eventually become public.

## LIBD

* `r Githubpkg("LieberInstitute/10xPilot_snRNAseq-human")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/10xPilot_snRNAseq-human)](https://github.com/LieberInstitute/10xPilot_snRNAseq-human/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/10xPilot_snRNAseq-human)](https://github.com/LieberInstitute/10xPilot_snRNAseq-human/pulls)

* `r Githubpkg("LieberInstitute/brain-epigenomics")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/brain-epigenomics)](https://github.com/LieberInstitute/brain-epigenomics/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/brain-epigenomics)](https://github.com/LieberInstitute/brain-epigenomics/pulls)

* `r Githubpkg("LieberInstitute/brainseq_phase2")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/brainseq_phase2)](https://github.com/LieberInstitute/brainseq_phase2/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/brainseq_phase2)](https://github.com/LieberInstitute/brainseq_phase2/pulls)

<!--
* `r Githubpkg("LieberInstitute/dbFinder")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/dbFinder)](https://github.com/LieberInstitute/dbFinder/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/dbFinder)](https://github.com/LieberInstitute/dbFinder/pulls)
-->

* `r Githubpkg("LieberInstitute/DLPFC_snRNAseq")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/DLPFC_snRNAseq)](https://github.com/LieberInstitute/DLPFC_snRNAseq/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/DLPFC_snRNAseq)](https://github.com/LieberInstitute/DLPFC_snRNAseq/pulls)

* `r Githubpkg("LieberInstitute/globus")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/globus)](https://github.com/LieberInstitute/globus/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/globus)](https://github.com/LieberInstitute/globus/pulls)

<!--
* `r Githubpkg("LieberInstitute/goesHyde_mdd_rnaseq")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/goesHyde_mdd_rnaseq)](https://github.com/LieberInstitute/goesHyde_mdd_rnaseq/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/goesHyde_mdd_rnaseq)](https://github.com/LieberInstitute/goesHyde_mdd_rnaseq/pulls)
-->

* `r Githubpkg("LieberInstitute/HumanPilot")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/HumanPilot)](https://github.com/LieberInstitute/HumanPilot/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/HumanPilot)](https://github.com/LieberInstitute/HumanPilot/pulls)

* `r Githubpkg("LieberInstitute/jhpce_module_config")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/jhpce_module_config)](https://github.com/LieberInstitute/jhpce_module_config/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/jhpce_module_config)](https://github.com/LieberInstitute/jhpce_module_config/pulls)

* `r Githubpkg("LieberInstitute/jhpce_mod_source")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/jhpce_mod_source)](https://github.com/LieberInstitute/jhpce_mod_source/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/jhpce_mod_source)](https://github.com/LieberInstitute/jhpce_mod_source/pulls)

* `r Githubpkg("LieberInstitute/qsva_brain")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/qsva_brain)](https://github.com/LieberInstitute/qsva_brain/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/qsva_brain)](https://github.com/LieberInstitute/qsva_brain/pulls)

* `r Githubpkg("LieberInstitute/spatialDLPFC")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/spatialDLPFC)](https://github.com/LieberInstitute/spatialDLPFC/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/spatialDLPFC)](https://github.com/LieberInstitute/spatialDLPFC/pulls)

* `r Githubpkg("LieberInstitute/SPEAQeasy")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/SPEAQeasy)](https://github.com/LieberInstitute/SPEAQeasy/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/SPEAQeasy)](https://github.com/LieberInstitute/SPEAQeasy/pulls)

* `r Githubpkg("LieberInstitute/SPEAQeasy-example")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/SPEAQeasy-example)](https://github.com/LieberInstitute/SPEAQeasy-example/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/SPEAQeasy-example)](https://github.com/LieberInstitute/SPEAQeasy-example/pulls)

<!--
* `r Githubpkg("LieberInstitute/twas")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/twas)](https://github.com/LieberInstitute/twas/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/twas)](https://github.com/LieberInstitute/twas/pulls)
-->

* `r Githubpkg("LieberInstitute/VistoSeg")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/VistoSeg)](https://github.com/LieberInstitute/VistoSeg/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/VistoSeg)](https://github.com/LieberInstitute/VistoSeg/pulls)

* `r Githubpkg("LieberInstitute/Visium_SPG_AD")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/Visium_SPG_AD)](https://github.com/LieberInstitute/Visium_SPG_AD/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/Visium_SPG_AD)](https://github.com/LieberInstitute/Visium_SPG_AD/pulls)

* `r Githubpkg("LieberInstitute/visiumStitched_brain")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/visiumStitched_brain)](https://github.com/LieberInstitute/visiumStitched_brain/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/visiumStitched_brain)](https://github.com/LieberInstitute/visiumStitched_brain/pulls)

* `r Githubpkg("LieberInstitute/zandiHyde_bipolar_rnaseq")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/zandiHyde_bipolar_rnaseq)](https://github.com/LieberInstitute/zandiHyde_bipolar_rnaseq/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/zandiHyde_bipolar_rnaseq)](https://github.com/LieberInstitute/zandiHyde_bipolar_rnaseq/pulls)

## `recount2` related

* `r Githubpkg("LieberInstitute/expr_shape")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/expr_shape)](https://github.com/LieberInstitute/expr_shape/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/expr_shape)](https://github.com/LieberInstitute/expr_shape/pulls)

* `r Githubpkg("LieberInstitute/insp")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/insp)](https://github.com/LieberInstitute/insp/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/insp)](https://github.com/LieberInstitute/insp/pulls)

* `r Githubpkg("LieberInstitute/marchionni_projects")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/marchionni_projects)](https://github.com/LieberInstitute/marchionni_projects/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/marchionni_projects)](https://github.com/LieberInstitute/marchionni_projects/pulls)

* `r Githubpkg("leekgroup/recount-analyses")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/recount-analyses)](https://github.com/leekgroup/recount-analyses/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/recount-analyses)](https://github.com/leekgroup/recount-analyses/pulls)

* `r Githubpkg("LieberInstitute/recount-brain")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recount-brain)](https://github.com/LieberInstitute/recount-brain/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/recount-brain)](https://github.com/LieberInstitute/recount-brain/pulls)

* `r Githubpkg("LieberInstitute/recount.bwtool")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recount.bwtool)](https://github.com/LieberInstitute/recount.bwtool/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/recount.bwtool)](https://github.com/LieberInstitute/recount.bwtool/pulls)

* `r Githubpkg("leekgroup/recount-contributions")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/recount-contributions)](https://github.com/leekgroup/recount-contributions/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/recount-contributions)](https://github.com/leekgroup/recount-contributions/pulls)

* `r Githubpkg("leekgroup/recount-website")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/recount-website)](https://github.com/leekgroup/recount-website/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/recount-website)](https://github.com/leekgroup/recount-website/pulls)

* `r Githubpkg("LieberInstitute/recount_pandey")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recount_pandey)](https://github.com/LieberInstitute/recount_pandey/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/recount_pandey)](https://github.com/LieberInstitute/recount_pandey/pulls)

* `r Githubpkg("LieberInstitute/recountWorkshop")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recountWorkshop)](https://github.com/LieberInstitute/recountWorkshop/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/recountWorkshop)](https://github.com/LieberInstitute/recountWorkshop/pulls)

* `r Githubpkg("LieberInstitute/recountWorkshop2019")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recountWorkshop2019)](https://github.com/LieberInstitute/recountWorkshop2019/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/recountWorkshop2019)](https://github.com/LieberInstitute/recountWorkshop2019/pulls)


* `r Githubpkg("LieberInstitute/recountWorkshop2020")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recountWorkshop2020)](https://github.com/LieberInstitute/recountWorkshop2020/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/recountWorkshop2020)](https://github.com/LieberInstitute/recountWorkshop2020/pulls)

* `r Githubpkg("LieberInstitute/ryten_work")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/ryten_work)](https://github.com/LieberInstitute/ryten_work/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/ryten_work)](https://github.com/LieberInstitute/ryten_work/pulls)

## `recount3` related

* `r Githubpkg("LieberInstitute/recount3-docs")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recount3-docs)](https://github.com/LieberInstitute/recount3-docs/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/recount3-docs)](https://github.com/LieberInstitute/recount3-docs/pulls)

## `derfinder` related

* `r Githubpkg("leekgroup/derSoftware")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/derSoftware)](https://github.com/leekgroup/derSoftware/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/derSoftware)](https://github.com/leekgroup/derSoftware/pulls)

* `r Githubpkg("leekgroup/derSupplement")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/derSupplement)](https://github.com/leekgroup/derSupplement/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/derSupplement)](https://github.com/leekgroup/derSupplement/pulls)

* `r Githubpkg("leekgroup/libd_n36")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/libd_n36)](https://github.com/leekgroup/libd_n36/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/libd_n36)](https://github.com/leekgroup/libd_n36/pulls)

* `r Githubpkg("leekgroup/regionReportSupp")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/regionReportSupp)](https://github.com/leekgroup/regionReportSupp/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/leekgroup/regionReportSupp)](https://github.com/leekgroup/regionReportSupp/pulls)

## Team related

* `r Githubpkg("lcolladotor/bioc_team_ds")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/bioc_team_ds)](https://github.com/lcolladotor/bioc_team_ds/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/bioc_team_ds)](https://github.com/lcolladotor/bioc_team_ds/pulls)

* `r Githubpkg("lcolladotor/DSgs_logs")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/DSgs_logs)](https://github.com/lcolladotor/DSgs_logs/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/DSgs_logs)](https://github.com/lcolladotor/DSgs_logs/pulls)

* `r Githubpkg("lcolladotor/lcolladotorsource")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/lcolladotorsource)](https://github.com/lcolladotor/lcolladotorsource/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/lcolladotorsource)](https://github.com/lcolladotor/lcolladotorsource/pulls)

<!-- * `r Githubpkg("lcolladotor/lcolladotor.github.com")` -->

<!-- [![GitHub issues](https://img.shields.io/github/issues/lcolladotor/lcolladotor.github.com)](https://github.com/lcolladotor/lcolladotor.github.com/issues) -->
<!-- [![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/lcolladotor.github.com)](https://github.com/lcolladotor/lcolladotor.github.com/pulls) -->


* `r Githubpkg("lcolladotor/team_faces")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/team_faces)](https://github.com/lcolladotor/team_faces/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/team_faces)](https://github.com/lcolladotor/team_faces/pulls)

* `r Githubpkg("lcolladotor/team_surveys")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/team_surveys)](https://github.com/lcolladotor/team_surveys/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/team_surveys)](https://github.com/lcolladotor/team_surveys/pulls)

# Misc

* `r Githubpkg("comunidadbioinfo/cdsbsource")`

[![GitHub issues](https://img.shields.io/github/issues/comunidadbioinfo/cdsbsource)](https://github.com/comunidadbioinfo/cdsbsource/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/comunidadbioinfo/cdsbsource)](https://github.com/comunidadbioinfo/cdsbsource/pulls)

* `r Githubpkg("lcolladotor/config_jhpce")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/config_jhpce)](https://github.com/lcolladotor/config_jhpce/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/config_jhpce)](https://github.com/lcolladotor/config_jhpce/pulls)

* `r Githubpkg("lcolladotor/cv")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/cv)](https://github.com/lcolladotor/cv/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/cv)](https://github.com/lcolladotor/cv/pulls)

* `r Githubpkg("lcolladotor/jhu-thesis-template")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/jhu-thesis-template)](https://github.com/lcolladotor/jhu-thesis-template/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/jhu-thesis-template)](https://github.com/lcolladotor/jhu-thesis-template/pulls)

* `r Githubpkg("lcolladotor/pkgs")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/pkgs)](https://github.com/lcolladotor/pkgs/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/pkgs)](https://github.com/lcolladotor/pkgs/pulls)

* `r Githubpkg("lcolladotor/twitter-stats")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/twitter-stats)](https://github.com/lcolladotor/twitter-stats/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/lcolladotor/twitter-stats)](https://github.com/lcolladotor/twitter-stats/pulls)

# Session info {.unnumbered}

```{r sessionInfo, echo=FALSE}
options(width = 120)
session_info()
```


<!-- Global site tag (gtag.js) - Google Analytics -->
<script async src="https://www.googletagmanager.com/gtag/js?id=UA-45299226-1"></script>
<script>
  window.dataLayer = window.dataLayer || [];
  function gtag(){dataLayer.push(arguments);}
  gtag('js', new Date());

  gtag('config', 'UA-45299226-1');
</script>

<center>	 
      <div id="clustrmaps-widget"></div><script type='text/javascript' id='clustrmaps' src='//cdn.clustrmaps.com/map_v2.js?cl=ffffff&w=300&t=m&d=Zo-deincaJGsqhqjIWsujtdoNOMJsnnZLefKmxDKVv8&co=124b73&cmo=dd53ff&cmn=4ec724'></script>
</center>
      
