---
title: "R packages by L. Collado-Torres"
author:
  - name: Leonardo Collado-Torres
    affiliation:
    - &libd Lieber Institute for Brain Development, Johns Hopkins Medical Campus
    - &ccb Center for Computational Biology, Johns Hopkins University
    email: lcolladotor@gmail.com
output:
  BiocStyle::html_document
abstract: |
  I like to check my R packages using GitHub Actions, Bioconductor and other
  tools. This small website helps me see the status of the packages I've made
  without having to navigate to a bunch of other websites.
vignette: |
  %\VignetteIndexEntry{R packages by L. Collado-Torres"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
library("BiocStyle")
library("sessioninfo")
```

# Bioconductor

## Maintainer

### Software

* `r Biocpkg("derfinder")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/derfinder.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/derfinder)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/derfinder.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/derfinder)
[![Codecov test coverage](https://codecov.io/gh/lcolladotor/derfinder/branch/master/graph/badge.svg)](https://codecov.io/gh/lcolladotor/derfinder?branch=master)
[![R build status](https://github.com/lcolladotor/derfinder/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/lcolladotor/derfinder/actions)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/derfinder.svg)](https://support.bioconductor.org/t/derfinder/)
[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/derfinder)](https://github.com/lcolladotor/derfinder/issues)

* `r Biocpkg("derfinderHelper")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/derfinderHelper.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/derfinderHelper)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/derfinderHelper.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/derfinderHelper)
[![Codecov test coverage](https://codecov.io/gh/leekgroup/derfinderHelper/branch/master/graph/badge.svg)](https://codecov.io/gh/leekgroup/derfinderHelper?branch=master)
[![R build status](https://github.com/leekgroup/derfinderHelper/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/leekgroup/derfinderHelper/actions)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/derfinderHelper.svg)](https://support.bioconductor.org/t/derfinderHelper/)
[![GitHub issues](https://img.shields.io/github/issues/leekgroup/derfinderHelper)](https://github.com/leekgroup/derfinderHelper/issues)

* `r Biocpkg("derfinderPlot")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/derfinderPlot.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/derfinderPlot)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/derfinderPlot.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/derfinderPlot)
[![Codecov test coverage](https://codecov.io/gh/leekgroup/derfinderPlot/branch/master/graph/badge.svg)](https://codecov.io/gh/leekgroup/derfinderPlot?branch=master)
[![R build status](https://github.com/leekgroup/derfinderPlot/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/leekgroup/derfinderPlot/actions)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/derfinderPlot.svg)](https://support.bioconductor.org/t/derfinderPlot/)
[![GitHub issues](https://img.shields.io/github/issues/leekgroup/derfinderPlot)](https://github.com/leekgroup/derfinderPlot/issues)

* `r Biocpkg("recount")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/recount.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/recount)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/recount.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/recount)
[![Codecov test coverage](https://codecov.io/gh/leekgroup/recount/branch/master/graph/badge.svg)](https://codecov.io/gh/leekgroup/recount?branch=master)
[![R build status](https://github.com/leekgroup/recount/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/leekgroup/recount/actions)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/recount.svg)](https://support.bioconductor.org/t/recount/)
[![GitHub issues](https://img.shields.io/github/issues/leekgroup/recount)](https://github.com/leekgroup/recount/issues)


* `r Biocpkg("regionReport")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/regionReport.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/regionReport)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/regionReport.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/regionReport)
[![R build status](https://github.com/leekgroup/regionReport/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/leekgroup/regionReport/actions)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/regionReport.svg)](https://support.bioconductor.org/t/regionReport/)
[![GitHub issues](https://img.shields.io/github/issues/leekgroup/regionReport)](https://github.com/leekgroup/regionReport/issues)

### Annotation

* `r Biocpkg("GenomicState")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://bioconductor.org/images/shields/availability/all.svg)](http://bioconductor.org/packages/release/data/annotation/html/GenomicState.html#archives)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/GenomicState/branch/master/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/GenomicState?branch=master)
[![R build status](https://github.com/LieberInstitute/GenomicState/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/LieberInstitute/GenomicState/actions)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/GenomicState.svg)](https://support.bioconductor.org/t/GenomicState/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/GenomicState)](https://github.com/LieberInstitute/GenomicState/issues)

### Experiment data

* `r Biocpkg("derfinderData")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://bioconductor.org/shields/build/release/data-experiment/derfinderData.svg)](http://bioconductor.org/checkResults/release/data-experiment-LATEST/derfinderData/)
[![BioC dev status](http://bioconductor.org/shields/build/devel/data-experiment/derfinderData.svg)](http://bioconductor.org/checkResults/devel/data-experiment-LATEST/derfinderData/)
[![R build status](https://github.com/leekgroup/derfinderData/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/leekgroup/derfinderData/actions)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/derfinderData.svg)](https://support.bioconductor.org/t/derfinderData/)
[![GitHub issues](https://img.shields.io/github/issues/leekgroup/derfinderData)](https://github.com/leekgroup/derfinderData/issues)

* `r Biocpkg("spatialLIBD")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://bioconductor.org/shields/build/release/data-experiment/spatialLIBD.svg)](http://bioconductor.org/checkResults/release/data-experiment-LATEST/spatialLIBD/)
[![BioC dev status](http://bioconductor.org/shields/build/devel/data-experiment/spatialLIBD.svg)](http://bioconductor.org/checkResults/devel/data-experiment-LATEST/spatialLIBD/)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/spatialLIBD/branch/master/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/spatialLIBD?branch=master)
[![R build status](https://github.com/LieberInstitute/spatialLIBD/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/LieberInstitute/spatialLIBD/actions)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/spatialLIBD.svg)](https://support.bioconductor.org/t/spatialLIBD/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/spatialLIBD)](https://github.com/LieberInstitute/spatialLIBD/issues)

### Workflow

* `r Biocpkg("recountWorkflow")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](https://master.bioconductor.org/shields/build/release/workflows/recountWorkflow.svg)](http://bioconductor.org/checkResults/release/workflows-LATEST/recountWorkflow/)
[![BioC dev status](https://master.bioconductor.org/shields/build/devel/workflows/recountWorkflow.svg)](http://bioconductor.org/checkResults/devel/workflows-LATEST/recountWorkflow/)
[![R build status](https://github.com/LieberInstitute/recountWorkflow/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/LieberInstitute/recountWorkflow/actions)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/recountWorkflow.svg)](https://support.bioconductor.org/t/recountWorkflow/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recountWorkflow)](https://github.com/LieberInstitute/recountWorkflow/issues)

## Contributor

* `r Biocpkg("brainflowprobes")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/brainflowprobes.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/brainflowprobes)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/brainflowprobes.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/brainflowprobes)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/brainflowprobes/branch/master/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/brainflowprobes?branch=master)
[![R build status](https://github.com/LieberInstitute/brainflowprobes/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/LieberInstitute/brainflowprobes/actions)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/brainflowprobes.svg)](https://support.bioconductor.org/t/brainflowprobes/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/brainflowprobes)](https://github.com/LieberInstitute/brainflowprobes/issues)

* `r Biocpkg("regutools")`

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/regutools.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/regutools)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/regutools.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/regutools)
[![Codecov test coverage](https://codecov.io/gh/ComunidadBioInfo/regutools/branch/master/graph/badge.svg)](https://codecov.io/gh/ComunidadBioInfo/regutools?branch=master)
[![R build status](https://github.com/ComunidadBioInfo/regutools/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/ComunidadBioInfo/regutools/actions)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/regutools.svg)](https://support.bioconductor.org/t/regutools/)
[![GitHub issues](https://img.shields.io/github/issues/comunidadbioinfo/regutools)](https://github.com/comunidadbioinfo/regutools/issues)

# GitHub

* `r Githubpkg("lcolladotor/biocthis")`

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/biocthis.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/biocthis)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/biocthis.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/biocthis)
[![R build status](https://github.com/lcolladotor/biocthis/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/lcolladotor/biocthis/actions)
[![Codecov test coverage](https://codecov.io/gh/lcolladotor/biocthis/branch/master/graph/badge.svg)](https://codecov.io/gh/lcolladotor/biocthis?branch=master)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/biocthis.svg)](https://support.bioconductor.org/t/biocthis/)
[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/biocthis)](https://github.com/lcolladotor/biocthis/issues)

`r Githubpkg("lcolladotor/dots")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/dots)](https://github.com/lcolladotor/dots/issues)

* `r Githubpkg("leekgroup/enrichedRanges")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/enrichedRanges)](https://github.com/leekgroup/enrichedRanges/issues)

* `r Githubpkg("LieberInstitute/jaffelab")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/jaffelab)](https://github.com/LieberInstitute/jaffelab/issues)

* `r Githubpkg("LieberInstitute/libdRSE")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/libdRSE)](https://github.com/LieberInstitute/libdRSE/issues)

* `r Githubpkg("LieberInstitute/recount3")`

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/recount3.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/recount3)
[![BioC dev status](http://www.bioconductor.org/shields/build/devel/bioc/recount3.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/recount3)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/recount3/branch/master/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/recount3?branch=master)
[![R build status](https://github.com/LieberInstitute/recount3/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/LieberInstitute/recount3/actions)
[![Support site activity, last 6 months: tagged questions/avg. answers per question/avg. comments per question/accepted answers, or 0 if no tagged posts.](http://www.bioconductor.org/shields/posts/recount3.svg)](https://support.bioconductor.org/t/recount3/)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recount3)](https://github.com/LieberInstitute/recount3/issues)

* `r Githubpkg("LieberInstitute/sgejobs")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/sgejobs)](https://github.com/LieberInstitute/sgejobs/issues)

* `r Githubpkg("LieberInstitute/shinycsv")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/shinycsv)](https://github.com/LieberInstitute/shinycsv/issues)


# Non R-packages

Note: some of these GitHub repositories are currently private but will eventually become public.

## LIBD

* `r Githubpkg("LieberInstitute/brain-epigenomics")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/brain-epigenomics)](https://github.com/LieberInstitute/brain-epigenomics/issues)

* `r Githubpkg("LieberInstitute/brainseq_phase2")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/brainseq_phase2)](https://github.com/LieberInstitute/brainseq_phase2/issues)

* `r Githubpkg("LieberInstitute/dbFinder")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/dbFinder)](https://github.com/LieberInstitute/dbFinder/issues)

* `r Githubpkg("LieberInstitute/globus")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/globus)](https://github.com/LieberInstitute/globus/issues)

* `r Githubpkg("LieberInstitute/goesHyde_mdd_rnaseq")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/goesHyde_mdd_rnaseq)](https://github.com/LieberInstitute/goesHyde_mdd_rnaseq/issues)

* `r Githubpkg("LieberInstitute/HumanPilot")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/HumanPilot)](https://github.com/LieberInstitute/HumanPilot/issues)

* `r Githubpkg("LieberInstitute/jaffe_onboarding")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/jaffe_onboarding)](https://github.com/LieberInstitute/jaffe_onboarding/issues)

* `r Githubpkg("LieberInstitute/jhpce_module_config")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/jhpce_module_config)](https://github.com/LieberInstitute/jhpce_module_config/issues)

* `r Githubpkg("LieberInstitute/jhpce_mod_source")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/jhpce_mod_source)](https://github.com/LieberInstitute/jhpce_mod_source/issues)

* `r Githubpkg("LieberInstitute/qsva_brain")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/qsva_brain)](https://github.com/LieberInstitute/qsva_brain/issues)

* `r Githubpkg("LieberInstitute/SPEAQeasy")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/SPEAQeasy)](https://github.com/LieberInstitute/SPEAQeasy/issues)

* `r Githubpkg("LieberInstitute/twas")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/twas)](https://github.com/LieberInstitute/twas/issues)


* `r Githubpkg("LieberInstitute/zandiHyde_bipolar_rnaseq")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/zandiHyde_bipolar_rnaseq)](https://github.com/LieberInstitute/zandiHyde_bipolar_rnaseq/issues)

## `recount2` related

* `r Githubpkg("LieberInstitute/expr_shape")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/expr_shape)](https://github.com/LieberInstitute/expr_shape/issues)

* `r Githubpkg("LieberInstitute/insp")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/insp)](https://github.com/LieberInstitute/insp/issues)

* `r Githubpkg("LieberInstitute/marchionni_projects")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/marchionni_projects)](https://github.com/LieberInstitute/marchionni_projects/issues)

* `r Githubpkg("leekgroup/recount-analyses")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/recount-analyses)](https://github.com/leekgroup/recount-analyses/issues)

* `r Githubpkg("LieberInstitute/recount-brain")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recount-brain)](https://github.com/LieberInstitute/recount-brain/issues)

* `r Githubpkg("LieberInstitute/recount.bwtool")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recount.bwtool)](https://github.com/LieberInstitute/recount.bwtool/issues)

* `r Githubpkg("leekgroup/recount-contributions")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/recount-contributions)](https://github.com/leekgroup/recount-contributions/issues)

* `r Githubpkg("leekgroup/recount-website")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/recount-website)](https://github.com/leekgroup/recount-website/issues)

* `r Githubpkg("LieberInstitute/recount_pandey")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recount_pandey)](https://github.com/LieberInstitute/recount_pandey/issues)

* `r Githubpkg("LieberInstitute/recountWorkshop")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recountWorkshop)](https://github.com/LieberInstitute/recountWorkshop/issues)

* `r Githubpkg("LieberInstitute/recountWorkshop2019")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recountWorkshop2019)](https://github.com/LieberInstitute/recountWorkshop2019/issues)

* `r Githubpkg("LieberInstitute/recountWorkshop2020")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/recountWorkshop2020)](https://github.com/LieberInstitute/recountWorkshop2020/issues)

* `r Githubpkg("LieberInstitute/ryten_work")`

[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/ryten_work)](https://github.com/LieberInstitute/ryten_work/issues)

## `derfinder` related

* `r Githubpkg("leekgroup/derSoftware")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/derSoftware)](https://github.com/leekgroup/derSoftware/issues)

* `r Githubpkg("leekgroup/derSupplement")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/derSupplement)](https://github.com/leekgroup/derSupplement/issues)

* `r Githubpkg("leekgroup/libd_n36")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/libd_n36)](https://github.com/leekgroup/libd_n36/issues)

* `r Githubpkg("leekgroup/regionReportSupp")`

[![GitHub issues](https://img.shields.io/github/issues/leekgroup/regionReportSupp)](https://github.com/leekgroup/regionReportSupp/issues)



# Misc

`r Githubpkg("comunidadbioinfo/cdsbsource")`

[![GitHub issues](https://img.shields.io/github/issues/comunidadbioinfo/cdsbsource)](https://github.com/comunidadbioinfo/cdsbsource/issues)

`r Githubpkg("lcolladotor/config_jhpce")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/config_jhpce)](https://github.com/lcolladotor/config_jhpce/issues)

`r Githubpkg("lcolladotor/cv")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/cv)](https://github.com/lcolladotor/cv/issues)

`r Githubpkg("lcolladotor/jhu-thesis-template")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/jhu-thesis-template)](https://github.com/lcolladotor/jhu-thesis-template/issues)

`r Githubpkg("lcolladotor/lcolladotorsource")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/lcolladotorsource)](https://github.com/lcolladotor/lcolladotorsource/issues)

`r Githubpkg("lcolladotor/pkgs")`

[![GitHub issues](https://img.shields.io/github/issues/lcolladotor/pkgs)](https://github.com/lcolladotor/pkgs/issues)



# Session info {.unnumbered}

```{r sessionInfo, echo=FALSE}
options(width = 120)
session_info()
```
